Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-03-16 paper.tex
up

The overall goal of this paper is to \textit{develop an general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality mode. We will achieve three objectives in this work as follows:

@@

\section{Comprehensive Quality Model}\label{Comprehensive_Quality_Model}
In this section, we propose a general comprehensive quality-aware service model in consideration of both semantic matchmaking quality and QoS for semantic web service composition.

\subsection{Comprehensive Quality Model}\label{qualityModel}
We propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation that ignores quality of semantic matchmaking.

@@

\textbf{Semantic web matchmaking quality model}. Due to that the discretisational characteristics of different match types and values assigned to matching types are driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for quality of parameter matchmaking, denoted as $mt_{p}$,  For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}. This formula (\ref{equation1}) is used to estimate the concept similarity between matching parameters, which is denoted as $s_{p}$. Therefore, given the quality of parameter matchmaking type and quality of parameter concept similarity, the quality of parameter matchmaking is defined by Formula (\ref{equation2}), where the value of $mt_{p}$ follows the same settings in \cite{lecue2009optimizing}. Particularly, 1 (Exact), 0.75 (Plugin), 0.5 (Subsume) or 0.25 (Intersection).

@@

\subsection{Objective Function}
In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions. It is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation8}). Note that weights can be adjusted according to users' preferences. The function value of 1 means the best comprehensive quality and 0 means the worst. For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1. Therefore, the service composition is try to maximise the value of objective function.
\vspace{-0.2cm}
\begin{equation}
\label{equation8}
Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent where $\sum_{i=1}^{6} w_i = 1$
\\
\vspace{-0.2cm}
\begin{equation}
\label{equation9}
\hat{Q_k} = 
\begin{cases}
	\frac{Q_k - Q_{k, min}}{Q_{k, max} - Q_{k, min}} & \text{ if }Q_{k, max} - Q_{k, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $k$ $=$ $1$, $2$, $3$, and $4$, where $Q_1$ as $MT$, $Q_2$ as $S$, $Q_3$ as $A$, and $Q_4$ as $R$.
\begin{equation}
\label{equation10}
\hat{Q_j} = 
\begin{cases}
	\frac{Q_{j,max} - Q_j}{Q_{j, max} - Q_{j, min}} & \text{ if }Q_{j, max} - Q_{j, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $j$ $=$ $1$, and $2$, where $Q_1$ as $T$ and $Q_2$ as $C$.

@@

We run the experiment on computing grid comprising of 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine. The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations. We run 30 times independently for each dataset. We configure weight of fitness function to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly. However, the settings of these weight values does not impact the method. In general, weight settings are adjusted according to users' preferences.

@@

\section{Conclusion}\label{conclusion}
This work introduces a general comprehensive evaluation model for considering semantic matchmaking quality and QoS. We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desired balance of both quality aspects. Also, we compare one GP-approach with our PSO-based method to show our performance results in finding more optimised solution. Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations that quality preference is not known.

>>>>

The overall goal of this paper is to \textit{develop an general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering both QoS optimisation and semantic matchmaking quality optimisation in our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality model. We will achieve three objectives in this work as follows:

@@

\section{Comprehensive Quality Model}\label{Comprehensive_Quality_Model}
In this section, we propose a general comprehensive quality-aware service model in consideration of both semantic matchmaking quality and QoS for semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware quality model that ignores quality of semantic matchmaking.

\subsection{Comprehensive Quality Model}\label{qualityModel}

@@

\textbf{Semantic web matchmaking quality model}. Due to that the discretisational characteristics of different match types and values assigned to matching types are driven by the cost of data integration and manipulation \cite{lecue2009optimizing}, partial ordering match types are considered to be one factor for quality of parameter matchmaking, denoted as $mt_{p}$,  For example, Exact matching type demands less time for computation compared to that of Plugin match. Another factor in our proposed model is concept similarity, which could be evaluated based on the edge counting method defined in \cite{shet2012new}. This formula (\ref{equation1}) is used to estimate the concept similarity between matching parameters, which is denoted as $s_{p}$. N1 and N2 measure the distances from an output-related concept and an input-related concept to the top node of a taxonomy respectively, and N measure the distances from the closest common ancestor of these two matched input-related and output-related concepts. $\lambda$ is set to 0 if we do not measure the similarities of neighbourhood concepts that is not the matching levels considered in this paper. Consequently, given the quality of parameter matchmaking type and quality of parameter concept similarity, the quality of parameter matchmaking is defined by Formula (\ref{equation2}).

@@

\subsection{Objective Function}
In real life, given a unique and optimised solution is always easier for customers to pick up directly when many quality criteria involved into decision making, rather than provided a set of solutions. It is very practical to define a single fitness as a weighted sum of all the quality related components in Formula (\ref{equation8}). Note that weights can be adjusted according to users' preferences. The function value of 1 means the best comprehensive quality and 0 means the worst. For this purpose, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the function value falls within the range from 0 to 1. Therefore, the service composition is try to maximise the value of objective function.
\vspace{-0.2cm}
\begin{equation}
\label{equation8}
Fitness = w_1 \hat{MT} + w_2 \hat{S} + w_3 \hat{A} + w_4 \hat{R} + w_5(1 - \hat{T}) + w_6(1 - \hat{C})
\end{equation}
\noindent where $\sum_{i=1}^{6} w_i = 1$
\\
\vspace{-0.2cm}
\begin{equation}
\label{equation9}
\hat{Q_k} = 
\begin{cases}
	\frac{Q_k - Q_{k, min}}{Q_{k, max} - Q_{k, min}} & \text{ if }Q_{k, max} - Q_{k, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $k$ $=$ $1$, $2$, $3$, and $4$, where $Q_1$ is $MT$, $Q_2$ is $S$, $Q_3$ is $A$, and $Q_4$ is $R$.
\begin{equation}
\label{equation10}
\hat{Q_j} = 
\begin{cases}
	\frac{Q_{j,max} - Q_j}{Q_{j, max} - Q_{j, min}} & \text{ if }Q_{j, max} - Q_{j, min} \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\noindent where $j$ $=$ $1$, and $2$, where $Q_1$ is $T$ and $Q_2$ is $C$.

@@

We run the experiment on computing grid comprising of 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine. The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, In particular, PSO population size is 30 with 100 generations. We run 30 times independently for each dataset. We configure weight of fitness function to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are set equally to 0.25, and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly. The $mt_{p}$ is set to 1 (Exact match) and 0.75 (Plugin). In general, weight settings and parameter match type quality are decided by users' preferences.

@@

\section{Conclusion}\label{conclusion}
This work introduces a general comprehensive evaluation model for considering semantic matchmaking quality and QoS. We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desired balance of both quality aspects. Also, we compare one GP-approach with our PSO-based method to show our performance results in finding more optimised solution. Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.
